---
title: "SummaryWidget"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: scroll
    theme: spacelab
    navbar:
      - { icon: "fa-github", href: "https://github.com/kent37/summarywidget", align: right }
---

```{r setup, include=FALSE}
library(flexdashboard)
knitr::opts_chunk$set(echo = TRUE)
```

Using
===================================== 
    
SummaryWidget is an [htmlwidget](http://www.htmlwidgets.org) which works with
[crosstalk](https://rstudio.github.io/crosstalk/index.html) to display a single
summary statistic which updates when the `crosstalk` selection changes. A SummaryWidget can display the count, sum or mean of one column of the selected data. 
It can also have a fixed filter that selects a subset of the full dataset.

#### Simple example

This code uses `crosstalk` to select from the `mtcars` database and 
a single `summarywidget` to report the number of cars selected. 

#### Install `crosstalk` and `summarywidget`

```
devtools::install_github("rstudio/crosstalk")
devtools::install_github("kent37/summarywidget")
```

#### Load libraries

```{r example1}
library(crosstalk)
library(summarywidget)
```

#### Create a crosstalk::SharedData object

```{r}
shared_mtcars = SharedData$new(mtcars)
```

#### Create a crosstalk checkbox

Click the checkboxes and see the count change below.

```{r}
filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE)
```

#### Show the number of cars selected

The default is to show a count of selected items.

```{r}
summarywidget(shared_mtcars)
```
   
Example
=====================================     

### Chart 1
    
