---
title: "SummaryWidget"
---

```{r setup, include=FALSE}
library(crosstalk)
library(DT)
library(summarywidget)

shared_mtcars = SharedData$new(mtcars[,c("mpg", "cyl", "hp", "am")])
```

SummaryWidget is an [HTML widget](http://www.htmlwidgets.org) which works with
[Crosstalk](https://rstudio.github.io/crosstalk/index.html) to display a single
summary statistic. The statistic updates when the Crosstalk selection changes. A SummaryWidget can display the count, sum or mean of one column of selected data. 
It can also have a fixed filter that selects a subset of the full dataset.

Try the example below. Click the checkboxes, manipulate the slider and
click rows in the data table. Watch the summary text update as the data selection changes.
The summary text uses four `summarywidget` instances to show four different summary statistics. 

-----

<big>You have selected **`r summarywidget(shared_mtcars)`** cars with an average mpg of
**`r summarywidget(shared_mtcars, 'mean', 'mpg', digits=1)`**. 
The **`r summarywidget(shared_mtcars, selection=~am==0)`** cars with automatic
transmission have an average mpg of 
**`r summarywidget(shared_mtcars, 'mean', 'mpg', selection=~am==0, digits=1)`**.</big>


```{r example, echo=FALSE}
bscols(widths = c(3,NA),
  list(
    filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE),
    filter_slider("hp", "Horsepower", shared_mtcars, ~hp, width = "100%")
  ),
  datatable(shared_mtcars, width=600, height=300, 
            options=list(pageLength=5, dom='tp'))
)
```

### Next steps

Read the [Using SummaryWidget](using.html) guide. See the [Extended Example](example.html) for another use.
