---
title: "Using SummaryWidget"
---

```{r setup, include=FALSE}
library(flexdashboard)
knitr::opts_chunk$set(echo = TRUE)
```

SummaryWidget reports summary statistics for a data set linked with Crosstalk-compatible [HTML widgets](http://htmlwidgets.org) within an R Markdown page or Shiny app. 

To begin, install the `summarywidget` and `crosstalk` packages:

```{r eval=FALSE}
devtools::install_github("kent37/summarywidget")
devtools::install_github("rstudio/crosstalk")
```

The `crosstalk` package includes widgets which control selection within a dataset.
You may also want to use other Crosstalk-compatible widgets; the [Crosstalk documentation](https://rstudio.github.io/crosstalk/) has a [list](https://rstudio.github.io/crosstalk/widgets.html). To keep this guide simple,
it uses a single `crosstalk::filter_checkbox` for selection.

<div>&nbsp;</div>

Crosstalk links widgets through an instance of `crosstalk::SharedData`. Here,
we share the `mtcars` data set.

```{r example1}
library(crosstalk)

shared_mtcars = SharedData$new(mtcars)
```

<div>&nbsp;</div>

A `crosstalk::filter_checkbox` allows selection from a categorical variable
such as the `Cylinders` column of the `shared_mtcars` data.

```{r}
filter_checkbox("cyl", "Cylinders", shared_mtcars, ~cyl, inline = TRUE)
```

Create a `summarywidget` with a reference to the shared data.
The `summarywidget` default statistic is a simple count of selected items. 
Click the checkboxes above to see the count change below.

```{r}
library(summarywidget)

summarywidget(shared_mtcars)
```

<div>&nbsp;</div>

A `summarywidget` can display a count, arithmetic mean or sum. To display
a sum or mean you must also specify the column to summarize. Here we show
the mean MPG for the selected cars. The `digits` parameter controls the number
of decimal digits displayed.

```{r}
summarywidget(shared_mtcars, statistic='mean', column='mpg', digits=1)
```

<div>&nbsp;</div>

You can also apply a filter to the initial data set and display a summary
restricted to the filtered data. Here we show the count of selected
cars with automatic transmission.

```{r}
summarywidget(shared_mtcars, selection=~am==0)
```

<div>&nbsp;</div>
  
Putting it all together, this example shows the average MPG for selected cars
with automatic transmission.

```{r}
summarywidget(shared_mtcars, 'mean', 'mpg', selection=~am==0, digits=1)
```

<div>&nbsp;</div>

The output of `summarywidget` is enclosed in a `<span>` tag so you can use it inline
in text. See the [Home](index.html) page for an example.
